\section{Introduction}
% Budget: 1/2 pages
Increasingly fine-grained billing for both netowrk~\cite{thimmaraju:2020} and computation resources~\cite{zhu:2017} is a notable recent trend, further acceleraged by the emergence of serverless computing~\cite{baldini:2017}.
~\cite{zhu:2017, thimmaraju:2020}
Such fine-grained billing creates strong incentives to develop and deploy applications that utilize a minimum amount of computing and network resources.
This calls for a novel approach in application development and deployment, allowing to trim down the use of computing and network resources.

\section{Architecture}

%TODO: 
% 1. New figure - Similar to Fig. 1 from Flowrider, maybe redrawn
% Architecture description (based on the Flowrider paper but _not_ copy-pasted
% Budget: 1/2 pages


\section{Use Cases and Demonstration}
%The demo aims to show a novel key distribution mechanism for cloud networks, which results in a reduced computation effort necessary to generate authentication credentials and establish secure communication between endpoints.
%The video consists of
The approach is reflected in scenario introduced below:
two endpoints establish a communication session over an OpenFlow switch.
Since there is no flow rule matching this network pattern, the switch upstreams the packet to the controller for inspection.
%TODO Further Clarify Use cases and demonstration
% Budget: 1/3 pages

\section{Future Work}
% v1 Done
We intend to further expand this work in several directions.
A first target is to adapt of the key sharing mechanism to other widely used network security protocol suites (primarily IPsec). 
Other future works includes verifying the mechanism's performance in hyperscale settings and integrating it with common cloud orchestration software.

\section{Acknowledgements}
% v1 Done
This work was financially supported in part by the Swedish Foundation for Strategic Research, with the grant RIT17-0035.
